### 2020-08-24 code/figureSM2.Rmd
load the mortality data to generate the supplemental figure

```
{r SM2}

>>>>

```{r SM2}

## mortality data from CDC:
namesmort = c("agerng","pdead","nsurv","ndie","pyrs","pyrsabove","expectedlife")
menmort = read_csv("../data/survival/lifetables/Table02.csv",skip=2)
## drop the final row, it's just a text info statement
menmort = menmort[1:NROW(menmort)-1,] 
wommort = read_csv("../data/survival/lifetables/Table03.csv",skip=2)
wommort = wommort[1:NROW(wommort)-1,]

names(menmort) = namesmort
names(wommort) = namesmort
yrs=seq(0,100,by=1);
menmort$yrnum = yrs
wommort$yrnum = yrs
